Ecuador plant species BIEN data

### 2023-01-23 code/L0/L0_Ecuador_plants_BIEN.Rmd
update html

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(mde)
library(DataExplorer)
library(summarytools)
library(bdvis)
```

# Get data for Ecuador from BIEN database
```{r}
# occurrence data
Ecuador_BIEN_occ <- BIEN_occurrence_country("Ecuador", all.taxonomy = TRUE, observation.type = TRUE, collection.info = TRUE)
# species list
Ecuador_BIEN_species_list <- BIEN_list_country(country = "Ecuador")
# trait data
Ecuador_BIEN_traits <- BIEN_trait_country("Ecuador", all.taxonomy = TRUE)
```

@@

## Data summary
```{r}
summary(Ecuador_BIEN_occ)
na_summary(Ecuador_BIEN_occ, exclude_cols = c("date_collected", "date_identified"))
```

```{r}
summary(Ecuador_BIEN_species_list)
na_summary(Ecuador_BIEN_species_list)
```

```{r}
summary(Ecuador_BIEN_traits)
na_summary(Ecuador_BIEN_traits)
```

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
```

@@

```{r}
plot_str(Ecuador_BIEN_traits)
introduce(Ecuador_BIEN_traits)
plot_intro(Ecuador_BIEN_traits)
plot_bar(Ecuador_BIEN_traits)
```

@@

>>>>

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(dplyr)
library(DataExplorer)
library(summarytools)
library(bdvis)
library(visdat)
```

# Get data for Ecuador from BIEN database
```{r}
# occurrence data
Ecuador_BIEN_occ <- BIEN_occurrence_country("Ecuador", all.taxonomy = TRUE, observation.type = TRUE, collection.info = TRUE, political.boundaries = TRUE, native.status = TRUE)
# species list
Ecuador_BIEN_species_list <- BIEN_list_country(country = "Ecuador")
# trait data
Ecuador_BIEN_traits <- BIEN_trait_country("Ecuador", all.taxonomy = TRUE, political.boundaries = TRUE, source.citation = TRUE)
```

@@

## Data summary
```{r}
summary(Ecuador_BIEN_occ)
```

```{r}
summary(Ecuador_BIEN_species_list)
```

```{r}
summary(Ecuador_BIEN_traits)
```

```{r}
glimpse(Ecuador_BIEN_occ)
```

```{r}
glimpse(Ecuador_BIEN_species_list)
```

```{r}
glimpse(Ecuador_BIEN_traits)
```

### using DataExplorer package
```{r}
plot_str(Ecuador_BIEN_occ)
introduce(Ecuador_BIEN_occ)
plot_intro(Ecuador_BIEN_occ)
plot_missing(Ecuador_BIEN_occ)
plot_bar(Ecuador_BIEN_occ)
```

@@

```{r}
plot_str(Ecuador_BIEN_traits)
introduce(Ecuador_BIEN_traits)
plot_intro(Ecuador_BIEN_traits)
plot_missing(Ecuador_BIEN_traits)
plot_bar(Ecuador_BIEN_traits)
```

@@

```{r}
#using visdat package
vis_dat(Ecuador_BIEN_occ, warn_large_data = FALSE)
vis_miss(Ecuador_BIEN_occ, warn_large_data = FALSE)
Ecuador_BIEN_occ %>%
  select_if(is.numeric)%>%
  vis_cor(warn_large_data = FALSE)
```

```{r}
#using visdat package
vis_dat(Ecuador_BIEN_traits, warn_large_data = FALSE)
vis_miss(Ecuador_BIEN_traits, warn_large_data = FALSE)
Ecuador_BIEN_traits %>%
  select_if(is.numeric)%>%
  vis_cor(warn_large_data = FALSE)
```
